This library contains functions that return information about its internal state, especially the amount of memory allocated from Vulkan. Please keep in mind that these functions need to traverse all internal data structures to gather these information, so they may be quite time-\/consuming. Don\textquotesingle{}t call them too often.\hypertarget{statistics_statistics_numeric_statistics}{}\section{Numeric statistics}\label{statistics_statistics_numeric_statistics}
You can query for overall statistics of the allocator using function vma\+Calculate\+Stats(). Information are returned using structure \hyperlink{structVmaStats}{Vma\+Stats}. It contains \hyperlink{structVmaStatInfo}{Vma\+Stat\+Info} -\/ number of allocated blocks, number of allocations (occupied ranges in these blocks), number of unused (free) ranges in these blocks, number of bytes used and unused (but still allocated from Vulkan) and other information. They are summed across memory heaps, memory types and total for whole allocator.

You can query for statistics of a custom pool using function vma\+Get\+Pool\+Stats(). Information are returned using structure \hyperlink{structVmaPoolStats}{Vma\+Pool\+Stats}.

You can query for information about specific allocation using function vma\+Get\+Allocation\+Info(). It fill structure \hyperlink{structVmaAllocationInfo}{Vma\+Allocation\+Info}.\hypertarget{statistics_statistics_json_dump}{}\section{J\+S\+O\+N dump}\label{statistics_statistics_json_dump}
You can dump internal state of the allocator to a string in J\+S\+ON format using function vma\+Build\+Stats\+String(). The result is guaranteed to be correct J\+S\+ON. It uses A\+N\+SI encoding. Any strings provided by user (see \hyperlink{allocation_annotation_allocation_names}{Allocation names}) are copied as-\/is and properly escaped for J\+S\+ON, so if they use U\+T\+F-\/8, I\+S\+O-\/8859-\/2 or any other encoding, this J\+S\+ON string can be treated as using this encoding. It must be freed using function vma\+Free\+Stats\+String().

The format of this J\+S\+ON string is not part of official documentation of the library, but it will not change in backward-\/incompatible way without increasing library major version number and appropriate mention in changelog.

The J\+S\+ON string contains all the data that can be obtained using vma\+Calculate\+Stats(). It can also contain detailed map of allocated memory blocks and their regions -\/ free and occupied by allocations. This allows e.\+g. to visualize the memory or assess fragmentation. 